Quality Metrics for SKOS Vocabularies

### 2012-03-13 background.tex
added citations

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}. \todo{CM}{check what the recent paper by Christophe Gueret is about.}

@@

After we identified an initial set of criteria, we formalized them into computable metrics and applied them on existing SKOS vocabularies to learn about the real-world occurrences of these criteria. During that process we also learned about additional quality issues in real world SKOS data, refined already identified criteria and included additional ones in a SKOS quality criteria catalogue, which we published at \url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}.

>>>>

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}. In the course of the LATC project, Gueret et al. propose an infrastructure that utilizes crowd-sourcing technology to semi-automatically create links between datasets of the LOD cloud. To ensure the quality of the resulting network, human judgement is supported by calculating a report of locally approximated network measures. \todo{BH}{ich denke antoine hat das paper gemeint: http://www.mendeley.com/download/public/18928/4084690763/56bdde328dfbba2cb8594b57152c0e132ef00a40/dl.pdf . Leider fehlen da etliche Details um sich ein konkretes Bild machen zu können}

@@

After we identified an initial set of criteria, we formalized them into computable metrics and applied them on existing SKOS vocabularies to learn about the real-world occurrences of these criteria. During that process we also learned about additional quality issues in real world SKOS data, refined already identified criteria and included additional ones in a SKOS quality criteria catalogue, which we published online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}}.

### 2012-03-13 introduction.tex
minor example fix
added citations

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards [\todo{cm}{ref}] or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

	\item \todo{CM}{An earlier version, the STW thesaurus (8.06) contained 5 pairs of concepts with identical labels}. As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.

>>>>

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

	\item An earlier version (v.8.06) of the STW thesaurus contained 5 pairs of concepts with identical labels. As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.
